\chapter{Introduction}
\authorAmSa
Some introducing words \dots
Zitierungen:

ganz normal inline im Text mit Seitenangaben \cite[6]{franke17}

oder an den Text in Klammern angehangen, mit Seitenangaben und Kommentar \autocites(see also his earlier work)[347-348]{franke17}


\section{Motivation}
Give a general overview on the subject of this thesis! In which context shall the content of this thesis \index{Thesis} be seen? 

Nutze autoref\{label\} ohne vorher Abbildung , figure, table oder sonstiges zu nutzen, z.B. \autoref{fig:Kossmat} oder \autoref{tab:Laser} und \autoref{equ:Boole's inequality} 

Am Anfang eines Satzes sollte Autoref\{label\} genutzt werden. Das ergibt einene ausgeschribene Referenz.

\Autoref{equ:Boole's inequality} zeigt die komplette Ausschreibung. Using $\pi$ is always advised.

Abkürzungen können im File AbbreviationDefinitions definiert werden und einfach über ac\{acronym\} abgerufen werden. Beim ersten Mal wird alles angezeigt: \ac{sundials} . Danach nur die Kurzform \ac{sundials}

\section{Research Goal}
What questions shall be investigated and answered in this thesis? What is the scope of this work?
\section{Outline of Work}
What is the structure of this thesis?
\lstset{language=java}
\begin{lstlisting}[caption={Code example for \LaTeX}]
\documentclass[
	appendixprefix=true,			% add the word appendix to the numeration of the chapters in the appendix
	BCOR=20mm,					% binding correction
	bibliography=totoc, 			% references in table of contents
    DIV=11,						% page division factor, see KOMA script documentation
    draft=false,						% status of document
    fontsize=11pt,				% font size
    headinclude=true,				% header is part of the type area
    headings=optiontohead,		% optional argument before chapter or section title appears in the header
    listof=chaptergapsmall,			% small vertical space between figures of different chapters in the lists of figures and tables
    listof=totoc,					% lists of figures and tables in table of contents
    numbers=noenddot,			% no second point in the numbering of figures, ...
%    open=right,					% chapter always starts on right side
    twoside,					% twoside or oneside document  
    paper=a4, 					% paper format
    parskip=half 				% distance between paragraphs
]{scrreprt}
\usepackage{graphicx}			% for including pictures
%\usepackage[draft]{graphicx}		% for including pictures in draft mode
\end{lstlisting}
